The demographic costs of sexually antagonistic selection in partially selfing populations

### 2022-01-05 doc/ResponseLetter-R1.tex

\begin{quote}
	{\itshape Thank you for this suggestion. To address this issue, as well as the Editor's request that we present population growth rates, we now start with an illustrative figure that has only one $f$, and that shows separately what happens to the allele frequencies (Population Genetic Outcome) and to the population growth rate (Demographic Outcome), see new {\bf fig. 1}. We hope that this will make it easier to interpret the old fig. 1, which is now {\bf fig. 2}. We have also included a new supplementary figure, {\bf fig. S1}, with detailed heatmaps for each of the parameter combinations presented in this figure (i.e., one $f$ per panel). However, we felt that this revised figure was to large and complicated to present in the main text (18 vs. 6 panels).}
\end{quote}

\noindent-- Maybe mention once, in a few words, what is meant by "segregate as a diallelic locus".
\begin{quote}
	{\itshape We have added a brief parenthesis to clarify ({\bf L.424--425}).}
\end{quote}

@@

\noindent-- Fig 4 : they are supposed to be dashed lines and dotted lines but all I see are dashed lines with various dashes. I found 4B in particular, hard to understand at first sight.

\begin{quote}
	{\itshape This figure now has four separate panels with heatmaps of $\lambda$, each with one set of invasion conditions ({\bf fig.~5}). We hope this eases interpretation.}
\end{quote}
\bigskip

@@

\noindent-- The 0s representing 0 matrices in eq 5 are not bold
\begin{quote}
	{\itshape Fixed}
\end{quote}

\noindent-- In same equation 1w is not defined
\begin{quote}
	{\itshape Fixed}
\end{quote}

\noindent-- Line 142, 2 "the"s
\begin{quote}
	{\itshape Fixed}
\end{quote}

\noindent-- Line 553 : not a typo, but the "was that how" in the middle of the sentence makes it hard to read
\begin{quote}
	{\itshape We have re-written this sentence to avoid this awkward phrasing ({\bf L.574--575}).}
\end{quote}
